Predicting Diabetes Based on Various Factors Using Machine Learning Models

### 2023-12-13 manuscript/manuscript.tex
Abstract formation

\begin{abstract}
This section will be completed once the paper is closer to completion. 
\end{abstract}

>>>>

\begin{abstract}
Each year, many patients are given the diagnosis of having diabetes and are left wondering what they could have done to prevent it. This
paper uses decision tree modeling to investigate which predictors of the Healthcare Diabetes dataset from kaggle are important in predicting 
an outcome of diabetes. In this study, after various exploratory data analysis, the data will be split into a training and testing set
that will be used to build a decision tree. The performance was evaluated using standard classification metrics, including accuracy, precision, 
recall, and F1 score. Our results provided that glucose level emerged as a robust predictor of diabetes. This study contributed to the growing body of
literature on diabetes prediction. These findings allow for early intervention measures, that can be used to provide a foundation for future research in diabetes
risk assessment.
\end{abstract}
